%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder \& CEO} % Job title
    {\href{https://www.speqt.co}{SPEQT}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jan. 2020 - PRESENT} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Building the next generation spend & cashflow management service for businesses}
    \end{cvitems}
}


%---------------------------------------------------------
  \cventry
    {Co-Founder \& CEO} % Job title
    {\href{https://www.xecolabs.com}{Xeco Labs}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jun. 2018 - PRESENT} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Building highly complex financial software}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder} % Job title
    {\href{https://www.initialblock.com}{Initial Block}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jan. 2018 - PRESENT} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Building world-class software solutions}
      \item {Consulting firms on tech management}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Backend Developer \& DevOps} % Job title
    {Hengroen} % Organization
    {Amsterdam, The Netherlands} % Location
    {Mar. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As part of the tech team I was involved in making the product ready for production-ready and high traffic, mainly by improvements on the overall infrastructure, writing stress tests and converting projects from JAVA to Golang.}
        \item {Keywords: Go, Golang, Java, Spring, AWS, Amazon ECS, Wercker, Terraform, Microservices, Docker}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Adviser} % Job title
    {Capture Camera International} % Organization
    {Amsterdam, The Netherlands} % Location
    {Apr. 2017 - May. 2017} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I helped and advised the team to move on preparations for the launch of the app. Basically my focus was to bring architectural changes to the backend and infrastructure for high availability / scalability.}
      \item {Keywords: Python, Django, Devops, Google Cloud, Postgres, Scalability, Docker}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Software Engineer \& DevOps} % Job title
    {\href{https://www.spaaza.com/}{Spaaza B.V.}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jan. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In charge of stabalizing SPAAZA's core infrastructure}
        \item {Designing the architecture and Developing SPAAZA's new Analytics Platform}
        \item {Keywords: Java, Spring, Golang, ElasticSearch, Serverless, Docker, AWS ECS, Machine Learning, DevOps, Terraform, Microservices}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.gingerpayments.com/}{Ginger Payments B.V.}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jul. 2016 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrating American Express as one of the supported payment providers for Ginger Platform}
        \item {Keywords: Python, Jython(Java), AWS Elastic Beanstalk, AWS DynamoDB, Microservices}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
  {Co-founder} % Job title
  {FIND A SHELF} % Organization
  {Amsterdam, The Netherlands} % Location
  {Sep. 2015 - Dec. 2016} % Date(s)
   {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {A platform connecting independent product makers and brands to retail stores}
            \item {An intensive mini M.B.A}
            \item {Keywords: Business Development, Sales and Marketing during the day, coding at night}
          \end{cvitems}
        }

%---------------------------------------------------------
  \cventry
    {Technical Consultant} % Job title
    {\href{https://d-tt.nl/}{DTT Multimedia}} % Organization
    {Amsterdam, The Netherlands} % Location
    {May 2016 - Jul. 2016} % Date(s)
      {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Coached the team to improve the workflow and work more agile}
            \item {Involved with a massive migration of servers to a cloud based environment}
            \item {Keywords: DevOps, Ansible, Consultancy, Agile, Scrum Master, AgileCoach}
          \end{cvitems}
        }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.coolgames.com/}{BoosterMedia (CoolGames.com)}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Mar. 2014 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In charge of scalibility of Boostermedia's multi region platform}
        \item {Designed and Developed the new Gaming Platform for company's flagship product CoolGames.com}
        \item {Designed and Developed the new state of the art Event Service to capture and analyse the gamers' behaviours}
        \item {Designed and Developed an analytics tool to gather and aggregate analytics data from 600+ Google Analytics accounts}
        \item {Keywords: Java8, Play Framework 2, Akka, Camel, ActiveMQ, Cassandra, Machine Learning, AWS, Packer}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Reviewer} % Job title
    {\href{https://www.packtpub.com/}{Packt Publishing}} % Organization
    {Birmingham, United Kingdom} % Location
    {Jun. 2015 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical reviewer of the book Java Functional Programming.}
        \item {Keywords: Technical Review, Java8, Functional Programming}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {\href{https://www.booking.com/}{Booking.com}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Dec. 2013 - Feb. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As part of the Hotel Innovation team, I was responsible for implementing new features for Booking.com's Extranet.}
        \item {Keywords: Perl, MySQL, JavaScript}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Developer} % Job title
    {\href{http://ebuddy.com/}{eBuddy B.V.}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Apr. 2013 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on various products and services such as XMS, GMS and APPX}
        \item {Developed a Smart Messaging concept, to analyze user's messages in real-time}
        \item {Keywords: Java, Spring, ElasticSearch, Cassandra, NLP, Puppet}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Language Technology Developer} % Job title
    {\href{http://gridline.nl}{GridLine}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jan. 2012 - Mar. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved and Developed various modules for the company's core products;Gridwalker-X: a lucene-based search engine; Gridwalker-R: Apache Mahout based recommendation System; Kilenkendetaal-QuickScan: service to measure the difficulty of text for Dutch language}
        \item {Worked on various projects for the Dutch government}
        \item {Keywords:Java, ApacheMahout, Apache Hadoop, Lucene, HBase, NLP, Machine Learning}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {\href{http://www.ua-foundation.org/}{United Academics}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Sep. 2011 - Dec. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part of developing the Social Media for the Academia}
        \item {Keywords: Python, Django, Javascript}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Researcher} % Job title
    {\href{http://www.parabots.nl//}{ParaBot Services}} % Organization
    {Amsterdam, The Netherlands} % Location
    {Jan. 2011 - Jul. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Sentiment Analysis service as part of my master's thesis: A Semi-supervised approach to context-based sentiment analysis}
        \item {Keywords: Python, Java, NLP, Machine Learning}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
